---
title: "Workflow of Running *Main_Simple_Figure1.R* and *Main_Simple_Table6.R*"
output:
  word_document: default
  pdf_document: default
---
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


## Workflow of Running *Main_Simple_Figure1.R*

### (1) Required Packages
First, install and load necessary packages. At the same time, source the necessary **semi_supervised_methods.R**, **SupervisedEstimation.R** and **dataGeneration.R** function files.  


```{r}
library(MASS)
library(caret)
library(quantreg)
source("semi_supervised_methods.R") 
source("dataGeneration.R")  
source("SupervisedEstimation.R")
```

### (2) Global Parameters
Then, we shall define some global parameters:

* n: the labelled data size and default is 250.  

* p: the dimension of predictor vector and default is 4. 

* option: the data setting and default is “i”. Here, "i" corresponds to setting (i) in Section 4.1 in our paper. We offer nine choices of "option": "i","ii","iii","W1","W2","W3",S1","S2","S3". These reminding choices correspond to settings (ii) - (iii) in Section 4.1 of the paper, 
 settings (W1) - (W2), settings (S1) - (S3) in Section 3.2 of the supplementary material 
in sequence. The parameter "option" is also used in the definition of the function *GenerateData* from the file **dataGeneration.R**. 

* tau_0: the quantile level, which is only useful for quantile regression working model, and  default is 0.5. 

* rep: the number of replications and default is 1000. 



```{r}
n=250  
p=4  
option="i"  
tau_0=0.5                        
rep=1000       
```

### (3) Replications
Next, we are going to (3.1) conduct the data generation, (3.2) use the selector GBIC_ppo to determine the polynomial order and (3.3) save the selected polynomial order in each replication. This procedure will be repeated "rep" times. 


```{r}
alpha_replications <- vector()
for (k in 1:rep)
{ 
  set.seed(k+20220122)
  #print(c("k",k))
  #######################(3.1) Data generation ##############################
  DesiredData<- GenerateData(n=n,p=p,option=option)
  data_labelled = DesiredData$Data.labelled  # the labelled data 
  #########################(3.2) GBIC_ppo ###################################
  # determine the type of working model by the quantity "option"
  if (option%in%c("i","W1","S1")){
    type= "linear" 
  } else if (option%in%c("ii","W2","S2")){
    type="logistic"
  } else if(option%in%c("iii","W3","S3")){
    type="quantile"
  }
  # data splitting 
  labelled_data_part1<- data_labelled[1:round(n/2),]
  labelled_data_part2<- data_labelled[(round(n/2)+1):n,]
  # the supervised estimate
  hattheta_supervised_part1<- SupervisedEst(labelled_data_part1,tau=tau_0,option=option)$Est.coef
  hattheta_supervised_part2<- SupervisedEst(labelled_data_part2,tau=tau_0,option=option)$Est.coef
  # the first derivative of the loss function L using the supervised estimate 
  L_first_derivative_part1<- L_first_derivative(labelled_data_part1,hattheta_supervised_part2,type=type,tau_level=tau_0)
  L_first_derivative_part2<- L_first_derivative(labelled_data_part2,hattheta_supervised_part1,type=type,tau_level=tau_0)
  # new data integrating the first derivatives of loss function
  Ynew<- rbind(L_first_derivative_part1,L_first_derivative_part2)
  covariates_labelled<- data_labelled[,-1]
  # GBIC_ppo to select the polynomial order 
  gamma=10
  GBICscrores<-apply(as.matrix(1:gamma,1,gamma), 1, function(t) GBIC_ppo(Ynew,covariates_labelled,t))
  alpha<- which.min(GBICscrores)
  ###################(3.3) save results ####################################
  alpha_replications <- c(alpha_replications,alpha)
}
```

### (4) Figures 
Last, plot the subfigure (a) in Figure 1. 

```{r}
#pdf("subfigure_GBIC_ppo.pdf")
df1<- data.frame(alpha_replications)
colnames(df1) <-"poly_order"
alpha1_plot<-ggplot(data = df1, mapping = aes(x =poly_order)) +
  geom_histogram( mapping = aes(x =poly_order),color="black", fill="white",bins=30)+
  labs(title=paste("Setting (",option,")",sep=""),x="Polynomial Order", y = "Frequency")
p1=alpha1_plot+ theme_bw() +theme(plot.title = element_text(hjust = 0)) +theme(aspect.ratio = 1)+
  theme(plot.title = element_text(size=10))+
  theme(panel.border = element_blank(),panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+scale_y_continuous(expand = c(0,0))
p1
```


## Workflow of Running *Main_Simple_Table6.R*

### (1) Required Packages
First, install and load necessary packages. At the same time, source the necessary **semi_supervised_methods.R**, **SupervisedEstimation.R** and **dataGeneration.R** function files.  

```{r}
library(MASS)
library(caret)
library(quantreg)
source("semi_supervised_methods.R") 
source("dataGeneration.R")  
source("SupervisedEstimation.R")
```

### (2) Global Parameters
Then, we shall define some global parameters:

* n: the labelled data size and default is 250.  

* N: the unlabelled data size and default is 500. 

* p: the dimension of predictor vector and default is 4. 

* option: the data setting and default is “ii”. Here, "ii" corresponds to setting (ii) in Section 4.1 in our paper.

* polyOrder: the polynomial order and default is 4. It is useful when we construct the polynomial functions of X as Z. Generally, we select the polynomial order by our proposed selector $\text{GBIC}_{ppo}$. Since this file is to run the subfigures, we use the same selected polynomial order for all replications under a specific polyorder. If the polynomial order isn't given, the main function of our method "PSSE" defined in the file **semi_supervised_methods.R** would select the polynomial order by the selector $\text{GBIC}_{ppo}$.

* tau_0: the quantile level, which is only useful for quantile regression working model, and  default is 0.5. 

* rep: the number of replications and default is 1000. 

```{r}
n=300
N=500 
p=7 
rep=1000 
option="ii"
polyOrder<- 4
tau_0=0.5
```

### (3) Target Parameter
We shall compute the true value of the target parameter by generating data of size $10^5$.

```{r}
set.seed(1230988)
LargeLabelledData<-GenerateData(n=10^5,p=p,option=option)$Data.labelled
target_parameter=SupervisedEst(LargeLabelledData,tau=tau_0,option=option)$Est.coef
```

### (4) Replications
Next, we are going to (4.1) conduct the data generation, (4.2) calculate the supervised estimate, (4.3) calculate all applicable semi-supervised estimates including ours, and (4.4) save results.
```{r}
results_supervised <- vector()
results_proposed <- vector()
results_PI<- vector()
results_EASE <- vector()
results_DRESS <- vector()
sd_proposed_matrix <- vector()
cp_proposed_matrix <- vector()
for (k in 1:rep)
{ 
  set.seed(k+20220122)
  #######################(4.1) Data generation ##############################
  DesiredData<- GenerateData(n=n,N=N,p=p,option=option)
  data_labelled = DesiredData$Data.labelled  # the labelled data 
  data_unlabelled = DesiredData$Data.unlabelled # the unlabelled data 
  #######################(4.2) supervised estimator #########################
  hattheta_supervised=SupervisedEst(data_labelled,tau=tau_0,option=option)$Est.coef
  ####################(4.3) semi-supervised estimators ######################
  ### determine the type of working model by the quantity "option"
  if (option%in%c("i","W1","S1")){
    type= "linear" 
  } else if (option%in%c("ii","W2","S2")){
    type="logistic"
  } else if(option%in%c("iii","W3","S3")){
    type="quantile"
  }
  ### our proposed one
  estimation_proposed <- PSSE(data_labelled,data_unlabelled,type=type,sd=TRUE,tau=tau_0,alpha=polyOrder)
  hattheta_proposed <- estimation_proposed$Hattheta  # coefficient estimate 
  sd_hattheta_proposed<- estimation_proposed$sd.of.hattheta # sd estimate 
  cp_hattheta_proposed<- (abs(hattheta_proposed-target_parameter)<=1.96*sd_hattheta_proposed) # coverage rate
  if (type=="linear"){
    ### PI proposed by Azriel et al. (2021)
    estimation_PI <- PI(data_labelled,data_unlabelled)
    hattheta_PI <- estimation_PI$Hattheta
    ### EASE proposed by Chakrabortty and Cai (2018)
    estimation_EASE <- EASE(data_labelled,data_unlabelled,K=5,H=40,r=2)
    hattheta_EASE <- estimation_EASE$Hattheta
  }else{
    hattheta_PI=NaN
    hattheta_EASE=NaN
  }
  ## DRESS proposed by Kawakita and Kanamori (2013) 
  estimation_DRESS<- DRESS(data_labelled,data_unlabelled,type=type,tau=tau_0,L=polyOrder)
  hattheta_DRESS <- estimation_DRESS$Hattheta
  ###################(4.4) save results ##########################
  results_supervised<-rbind(results_supervised,hattheta_supervised) 
  results_proposed <- rbind(results_proposed,hattheta_proposed)
  results_PI <- rbind(results_PI,hattheta_PI)
  results_EASE <- rbind(results_EASE,hattheta_EASE)
  results_DRESS <- rbind(results_DRESS,hattheta_DRESS)
  sd_proposed_matrix<- rbind(sd_proposed_matrix,sd_hattheta_proposed)
  cp_proposed_matrix<- rbind(cp_proposed_matrix,cp_hattheta_proposed)
}
```

### Tables
Last, obtain the subtable (the first eight rows) in Table 6. 
```{r}
results_total <- round(cbind(target_parameter,
                       colMeans(results_supervised)-target_parameter,apply(results_supervised,2,sd),
                       colMeans(results_PI)-target_parameter,apply(results_PI,2,sd), apply(results_supervised,2,var)/apply(results_PI,2,var),
                       colMeans(results_EASE)-target_parameter,apply(results_EASE,2,sd),apply(results_supervised,2,var)/apply(results_EASE,2,var),
                       colMeans(results_DRESS)-target_parameter,apply(results_DRESS,2,sd),apply(results_supervised,2,var)/apply(results_DRESS,2,var),
                       colMeans(results_proposed)-target_parameter,apply(results_proposed,2,sd),apply(results_supervised,2,var)/apply(results_proposed,2,var),
                       colMeans(sd_proposed_matrix),colMeans(cp_proposed_matrix)
),3)
colnames(results_total) <- c("real_value","bias","SE","bias","SE","ARE","bias","SE","ARE","bias","SE","ARE","bias","SE","ARE","SEE","CP")
rownames(results_total) <-NULL
cat("Methods: supervised, PI, EASE, DRESS, proposed\n")
cat(paste("The setting of (p,n,N):",p,n,N,sep=" "))
cat("\n")
print(results_total)
```




